### 2014-10-16 excersice 1/main.tex
redid

\usepackage{listings}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{fancyhdr}
\usepackage[margin=1in]{geometry}
\pagestyle{fancy}

@@

\begin{document}

\section*{Q1}
\begin{enumerate}
\item % a
The goal of the algorithm in Listing 1 is to group n points into m clusters. This is done by invoking the function \texttt{kernel} until its return value \texttt{delta} is equal to 0. In \texttt{kernel} all points are itterated over to find which one of the m clusters supplied in \texttt{clusters} is closest. To find the closest cluster all clusters are itterated over in \texttt{find\_nearest\_point} and the Euclidean distance is calulated in \texttt{euclid\_dist\_2}. When all clusters have been itterated over the index of the cloest one is returned to \texttt{kernel}. This index is used to check if the point already belongs to this cluster, if not delta is increased to indicate that a point have changed cluster. To calulate the center of each cluster an average of the cooridnates for all points belonging to the cluster are calulated.

@@

\item % d
A more fine grained solution than the one presented in (c) is shown in listing~\ref{lst:kernelfine} where the \texttt{atomic} directive is used on each of the critical varaibles. As explained in (c) only \texttt{new\_centers} and \texttt{new\_centers\_len} need this protection so two locks is enough.

\end{enumerate}
\lstset{language=C,frame=single}
\lstinputlisting[lastline=31, caption={Modified kernel coarse grained},label={lst:kernelcoarse}]{upgC.c}
\lstinputlisting[firstline=32, caption={Modified kernel fine grained},label={lst:kernelfine}]{upgC.c}

\section*{Q2}
The request write/read sequence will be as follows: \\

@@

\lstset{language={[x86masm]Assembler},frame=single}
\lstinputlisting[firstline=24, lastline=36, caption={Sync. using T\&S},label={lst:q4b}]{upgASM.asm}
\lstinputlisting[firstline=39, lastline=44, caption={Sync. using F\&A},label={lst:q4c}]{upgASM.asm}

\section*{Q5} % 7.3
\begin{enumerate}
\item % a
See listing~\ref{lst:q5a}.
\setcounter{enumi}{3}
\item % d
See listing~\ref{lst:q5d}.
\item % e
See listing~\ref{lst:q5e}.
\end{enumerate}

\lstset{language={[x86masm]Assembler},frame=single}
\lstinputlisting[firstline=2, lastline=5, caption={F\&ADD X, Rx, a},label={lst:q5a}]{upgASM.asm}

\lstinputlisting[firstline=8, lastline=12, caption={SWAP(Rx, X)},label={lst:q5d}]{upgASM.asm}

\lstinputlisting[firstline=15, lastline=21, caption={CAS Rx, Ry, X},label={lst:q5e}]{upgASM.asm}

>>>>

\usepackage{listings}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{fancyhdr}
\usepackage[margin=1in]{geometry}
\usepackage{color}
\pagestyle{fancy}

@@

\begin{document}
\textcolor{red}{\huge Changed stuff marked in red.}
\section*{Q1}
\begin{enumerate}
\item % a
The goal of the algorithm in Listing 1 is to group n points into m clusters. This is done by invoking the function \texttt{kernel} until its return value \texttt{delta} is equal to 0. In \texttt{kernel} all points are itterated over to find which one of the m clusters supplied in \texttt{clusters} is closest. To find the closest cluster all clusters are itterated over in \texttt{find\_nearest\_point} and the Euclidean distance is calulated in \texttt{euclid\_dist\_2}. When all clusters have been itterated over the index of the cloest one is returned to \texttt{kernel}. This index is used to check if the point already belongs to this cluster, if not delta is increased to indicate that a point have changed cluster. To calulate the center of each cluster an average of the cooridnates for all points belonging to the cluster are calulated.

@@

\item % d
\textcolor{red}{
A more fine grained solution than the one presented in (c) is shown in listing~\ref{lst:kernelfine} where \texttt{OpenMP}s runtime locks have been used. As explained in (c) \texttt{new\_centers} and \texttt{new\_centers\_len} need protection an now also \texttt{delta} as we no longer use the \texttt{reduction} directive. As we protext every singel address new no need $ 1 + 3 \times nclusters$ locks in total.
}

\end{enumerate}
\lstset{language=C,frame=single}
\lstinputlisting[lastline=31, caption={Modified kernel coarse grained},label={lst:kernelcoarse}]{upgC.c}
\textcolor{red}{
\lstinputlisting[firstline=32, caption={Modified kernel fine grained},label={lst:kernelfine}]{upgC.c}
}
\section*{Q2}
The request write/read sequence will be as follows: \\

@@

\lstset{language={[x86masm]Assembler},frame=single}
\lstinputlisting[firstline=24, lastline=36, caption={Sync. using T\&S},label={lst:q4b}]{upgASM.asm}
\textcolor{red}{
\lstinputlisting[firstline=39, lastline=44, caption={Sync. using F\&A},label={lst:q4c}]{upgASM.asm}
}
\section*{Q5} % 7.3
\begin{enumerate}
\item % a
See listing~\ref{lst:q5a}.
\setcounter{enumi}{3}
\item % d
See listing~\ref{lst:q5d}.
\item % e
See listing~\ref{lst:q5e}.
\end{enumerate}

\lstset{language={[x86masm]Assembler},frame=single}
\textcolor{red}{
\lstinputlisting[firstline=2, lastline=5, caption={F\&ADD X, Rx, a},label={lst:q5a}]{upgASM.asm}
}
\textcolor{red}{
\lstinputlisting[firstline=8, lastline=12, caption={SWAP(Rx, X)},label={lst:q5d}]{upgASM.asm}
}
\textcolor{red}{
\lstinputlisting[firstline=15, lastline=21, caption={CAS Rx, Ry, X},label={lst:q5e}]{upgASM.asm}
}
